---
title: "Lecture_4_Distribution_of_RVs"
author: "Parthsarthy Nandi"
date: "2022-12-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
      download.file("http://www.openintro.org/stat/data/bdims.RData", destfile = "bdims.RData")
      load("bdims.RData")
      mdims <- subset(bdims, sex == 1)
      fdims <- subset(bdims, sex == 0)

```

# On Your Own

.Now let's consider some of the other variables in the body dimensions data set.
 Using the figures at the end of the exercises, match the histogram to its normal probability plot. 
 All of the variables have been standardized (first subtract the mean, then divide by the 
 standard deviation), so the units won't be of any help.
 If you are uncertain based on these figures, generate the plots in R to check. (B,C,D)

a. The histogram for female biiliac (pelvic) diameter ( bii.di ) belongs to normal probability plot letter ____.
```{r}
      qqnorm(fdims$bii.di)
      qqline(fdims$bii.di)
```

    B
b. The histogram for female elbow diameter ( elb.di ) belongs to normal probability plot letter ____.
```{r}
      qqnorm(fdims$elb.di)
      qqline(fdims$elb.di)
```

    C
c. The histogram for general age ( age ) belongs to normal probability plot letter ____.
```{r}
      qqnorm(fdims$age)
      qqline(fdims$age)
```

    D
d. The histogram for female chest depth ( che.de ) belongs to normal probability plot letter ____.
```{r}
      qqnorm(fdims$che.de)
      qqline(fdims$che.de)
```

    A
.Note that normal probability plots C and D have a slight stepwise pattern.
Why do you think this is the case?

    In my opinion it is stepwise as both are related to time and stage of life of females.
.As you can see, normal probability plots can be used both to assess normality and visualize skewness.
Make a normal probability plot for female knee diameter ( kne.di ).
Based on this normal probability plot, is this variable left skewed, symmetric, or right skewed?
Use a histogram to confirm your findings.
```{r}
      qqnorm(fdims$kne.di)
      qqline(fdims$kne.di)
```
```{r}
      hist(fdims$kne.di, breaks = 15)
```

    Right Skewed after verifing with the hist. Which is prominent from Normal and supported by hist.
B
qqnorm(fdims$bii.di)
qqline(fdims$bii.di)

C
qqnorm(fdims$elb.di)
qqline(fdims$elb.di)

D
qqnorm(fdims$age)
qqline(fdims$age)

A
qqnorm(fdims$che.de)
qqline(fdims$che.de)
