---
title: "Lecture2"
author: "Parthsarthy Nandi"
date: "2022-12-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("http://www.openintro.org/stat/data/cdc.R")
```


###  NOW ON YOUR OWN....
#.	Make a scatterplot of weight versus desired weight. Describe the relationship between these two variables.
```{r}
plot( cdc$weight , cdc$wtdesire  )  
```
    
    Here we can conclude that there is a negative linear relationship between weight and desired weight. As we can see as weight is increasing desired weight is decreasing. This say that people who are between 200-300 have a desired weight of 100-200.


#.	Let's consider a new variable: the difference between desired weight (wtdesire) and current weight (weight).
#.  Create this new variable by subtracting the two columns in the data frame and assigning them to a new object called wdiff.
```{r}
wdiff = cdc$wtdesire - cdc$weight
head(wdiff,n=10)
```


#.	What type of data is wdiff? If an observation wdiff is 0, what does this mean about the person's weight and desired weight.
```{r}
class(wdiff)
```
    If a persons weight is 0 it means the person's weight and desired weight is same.
#.  What if wdiff is positive or negative?
    If negative person has to lose weight and if Positive he has to gain weight.
    
#.	Describe the distribution of wdiff in terms of its center, shape, and spread, including any plots you use.

```{r}
#table(wdiff)
plot(table(wdiff))
boxplot(wdiff)
hist(wdiff)
summary(wdiff)
```
    After plotting boxplot and histogram we see that maximum people are happy with their weight. Most people wants to loose weight than to gain weight.
#.  What does this tell us about how people feel about their current weight?
    Most are satisfied. As the Mode is 5616(I checked this using > table(wdiff)).
#.	Using  mumerical summaries and a side-by-side box plot, determine if men tend to view their weight differently than women.
```{r}
cdc_male = subset(wdiff,cdc$gender == 'm')
cdc_female = subset(wdiff,cdc$gender == 'f')
summary(cdc_male)
summary(cdc_female)
boxplot(wdiff ~ cdc$gender)
```
#.	Now it's time to get creative. Find the mean and standard deviation of weight and determine 
#.  what proportion of the weights are within one standard deviation of the mean.
```{r}
cdc_mean <- mean(cdc$weight)
cdc_sd <- sd(cdc$weight)
cdc_one_sd <- subset(cdc, cdc$weight>(cdc_mean-cdc_sd) & cdc$weight<(cdc_mean+cdc_sd))
nrow(cdc_one_sd)/nrow(cdc)*100
```
    Therefore 70.76 % are within one standard deviation.
